The eclipse of ASASSN-21qj

### 2022-12-22 src/tex/ms.tex
[showyourwork]
[showyourwork] overleaf sync

\begin{figure*}
   \begin{centering}
   \includegraphics[width=\textwidth]{figures/eclipse_overview2.pdf}
      \caption{Photometry from the optical bands of the eclipse.
      %
The different telescopes and filters are indicated in the legend.
%
Each light curve is offset vertically by 0.8.
              }
        \label{fig:eclipse_overview}
        \script{plot_eclipse_overview2.py}
    \end{centering}
\end{figure*}

@@

Looking for periodic stellar activity, the periodogram for the pre-eclipse light curve is shown from 0 to 50 days in the lower panel.
%
Here we see significant periods at around 6.5 and 11 days, which we attribute to light curve modulation due to starspots rotating in and out of view.

>>>>

\begin{figure*}
   \begin{centering}
   \includegraphics[width=\textwidth]{figures/master_lightcurve_rvc.pdf}
      \caption{Richelle figure
              }
        \label{fig:eclipse_overview}
        \script{plot_master_lightcurve.py}
    \end{centering}
\end{figure*}

@@

Looking for periodic stellar activity, the periodogram for the pre-eclipse light curve is shown from 0 to 50 days in the lower panel.
%
Here we see significant periods at around 6.5 and 11 days, which we attribute to light curve modulation caused by starspots rotating in and out of view.
